\plaintitle

### 2016-09-06 drafts/labor/complexity.tex
various additions to slicing.tex; still adding to piecework perspective

\subsubsubsection{\whatchanged}
\topic{Digital media have expanded the scope of
viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity.
Given the flourishing of on--demand labor platforms such as
Uber, Amazon Mechanical Turk, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the Internet has trivialized
the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of
        ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code}
\end{inlinelist}.

@@

\topic{Crowdsourcing falters when the routinization of complex work proves difficult.}
\ali{Something about complexity being difficult to make routine when
there are lots of little tasks a la \citeauthor{Brown01041990}}

>>>>

\subsubsubsection{\whatchanged}
\topic{Digital media have expanded the scope of
viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity
\cite{Brown01041990}.
Given the flourishing of on--demand labor platforms such as
Uber, AMT, and others, we ask ourselves
what --- if anything --- has changed.
We argue that
the Internet has trivialized
the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of
        ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code,miller2011understanding}
\end{inlinelist}.

@@

\topic{Crowdsourcing falters when the routinization of complex work proves difficult.}
\ali{Something about complexity being difficult to make routine when
there are lots of little, varied, unpredictable tasks (nod to \citeauthor{Brown01041990})}

### 2016-09-06 drafts/labor/introduction.tex
slicing and flexibility spin-off
various additions to slicing.tex; still adding to piecework perspective

\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item What are the limits of crowdsourcing
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,embracingErrorKrishna,
              Nebeling:2016:WCW:2858036.2858169,Hahn:2016:KAB:2858036.2858364}?
        \note{Perhaps to be more precise, we ask two questions here:
                \begin{enumerate}
                  \item how far will crowdsourcing reach into the everyday lives of people, and
                  \item how complex can crowdwork become?
                \end{enumerate}}
  \item What forms of work design, and worker management and arrangement, are viable?
        \cite{bernsteinSoylent,sensitiveTasks,LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,whyWouldAnyoneBrewer,
              takingAHITMcInnis}
\end{enumerate}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  \nobalance{}
  \clearpage
  \begin{appendices}
  \section{Sleeping kittens}
  \theendnotes
  \end{appendices}

>>>>

\topic{The extant body of work has ostensibly sought to answer one underlying question:
What does the future hold for work and those that do it?}
Researchers have offered their input on this open question along three major threads:
\begin{enumerate}
  \item What are the limits of crowdsourcing?
        Specifically,
        \begin{inlinelist}
          \item how complex can crowd work get? and
          \item how far will crowd work reach into the everyday lives of people?
        \end{inlinelist}
        \cite{foundry,suzukiAtelier,KimStoria,yuanAlmost,YuEncouragingOutside,
              Nebeling:2016:WCW:2858036.2858169,
              Hahn:2016:KAB:2858036.2858364};
  \item To what extent can we decompose work (especially into micro--tasks)?
        \cite{embracingErrorKrishna,bernsteinSoylent,sensitiveTasks,
              LykourentzouPersonalityMatters,KucherbaevReLauncher,
              Law:2016:CKC:2858036.2858144,Cai:2016:CRI:2858036.2858237,
              Chang:2016:ACC:2858036.2858411,Newell:2016:OMA:2858036.2858490}; and%
  \item What will work and the place of work look like for the workers?
        \cite{turkopticon,storiesIraniSilberman,dynamo,crowdcollab,
              whyWouldAnyoneBrewer,takingAHITMcInnis}
\end{enumerate}

@@

\onlyinsubfile{
  \balance{}
  \printbibliography
  \nobalance{}
  % \clearpage
  % \begin{appendices}
  % \section{Sleeping kittens}
  % \end{appendices}

### 2016-09-06 drafts/labor/slicing.tex
various additions to slicing.tex; still adding to piecework perspective

Concurrent with the body of work on the complexity of crowdsourcing
has been a thread of work exploring the decomposition of work.
In this section we'll discuss some of the approaches and the results 
the crowdsourcing community have taken from their work.
Then, as previously,
we'll discuss some of the findings that piecework research
has yielded.
Finally, we'll discuss similarities and differences between crowdwork and piecework,
and how crowdwork's limitations and potential differ from piecework's.

\subsubsubsection{\crowdworkpers}
\topic{The research on crowdwork and decomposition has generally driven toward finding new ways
to strip unnecessary context from work,
allowing tasks to be broken down into smaller parts.}
As \citeauthor{verroios2014context} frame it,
``the crowd must be able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
Researchers have thus investigated the role of
distributed, contextually independent work
in the contexts of collaborative writing of various forms,
software development,
classification, and myriad other purposes
\cite{Kittur:2009:CCI:1518701.1518928,Baecker:1993:UID:169059.169312,
      10.2307/1562247,karnin2010crowdsourcing,bragg2013crowdsourcing,
      chilton2013cascade}.

\topic{One of the emergent properties of micro--tasks has been the relative cost of
\textit{finding} worthwhile tasks.}
The research community has documented and to some extent attempted to intervene in
the discovery of worthwhile tasks
\cite{taskSearch}.
\citeauthor{Cosley:2007:SUI:1216295.1216309}
attempts to address this by
directing workers to tasks through
``intelligent task routing''
\cite{Cosley:2007:SUI:1216295.1216309}.
Much of this work and the work at the periphery of this space, then,
has focused on
minimizing the amount of time that people need to spend doing
anything other than the work for which they are paid.

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item each task was quickly verifiable by a qualified [human] computer,
  \item tasks were discrete --- independent from one another, and
  \item knowledge of the full scope of the project --- indeed, knowledge of anything more than the problem set at hand ---
  was wholly unnecessary.
\end{enumerate}

@@

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management,
            and how piecework literature tried to measure everything,
            but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}
  \end{appendices}
}

>>>>

\subsubsubsection{\crowdworkpers}
% \ali{Does this belong here at all? The complexity argument just dives in.}
\topic{The crowdsourcing research into work decomposition
has largely focused on minimizing the additional context necessary to do tasks,
and making it easier to do tasks with less time.}
This first thread is
perhaps best described by \citeauthor{verroios2014context} as
making crowd workers ``\dots able to act with
global understanding when each contributor only has access to local views''
\cite{verroios2014context}.
With the exception of a few cases
(specifically, \citeauthor{Kinnaird:2012:WTM:2389176.2389219}'s work
which finds that greater work context fosters more reliably high--quality work),
the micro task paradigm has emerged as the overwhelming favorite
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,
      cheng2015break,Kinnaird:2012:WTM:2389176.2389219}.

\topic{As the additional context necessary to complete a task diminishes,
the marginal cost of finding and
\textit{doing} tasks has increasingly become the focus of research.}
\citeauthor{taskSearch} illustrate the challenges on AMT,
and some work has gone into ameliorating the problems specific to this work site
(\textit{ReLauncher}), % does anyone care for project names?
while other work designs tasks around gap time
(\textit{Twitch Crowdsourcing} \& \textit{Wait--Learning})
\cite{taskSearch,KucherbaevReLauncher,Vaish:2014:TCC:2611222.2556996,
      Cai:2015:WLW:2702123.2702267}.
Yet more work looks at the general framing of tasks,
chaining and arranging them to maximally exploit
the attention and stress threshold % ???
of workers
\cite{Cai:2016:CRI:2858036.2858237}.
Rather than attempt to minimize the error rates in micro--tasks,
as \citeauthor{Kinnaird:2012:WTM:2389176.2389219} suggested,
we as a community have leaned \textit{into} the peril of
low--context work,
``embracing error'' in crowdsourcing
\cite{embracingErrorKrishna}.

Not all of the work toward optimizing crowd work--flows has gone toward
minimizing the creative input of crowd workers;
a thriving body of literature adopts
practices such as pipelining to allow experts to participate in crowd work
\cite{foundry}.

\subsubsubsection{\pieceworkpers}
The beginnings of systematized task decomposition stretch back as far as the \nth{17} century,
when Airy employed young boys at the Greenwich Observatory who
``possessed the basic skills of mathematics, including
`Arithmetic, the use of Logarithms, and Elementary Algebra'~''
to \textit{compute} astronomical phenomena
\cite{grier2013computers}.
Airy's tasks were unique at the time for several reasons:
\begin{enumerate}
  \item Each task was quickly verifiable by a qualified (human) computer;
  \item tasks were discrete --- that is, independent from one another; and
  \item knowledge of the full scope of the project
  --- indeed, knowledge of anything more than the problem set at hand ---
  was unnecessary.
\end{enumerate}

@@

    My goal for this section is to make two points:
    \begin{enumerate}
      \item show how this is related to the assembly line and scientific management,
            and how piecework literature tried to measure everything,
            but found it untenable given the extra equipment that was necessary
            (but generally which didn't exist)
            to track every movement and action that workers took.
      \item show how this work was enabled by the ``verifiability'' of work output(?)
    \end{enumerate}

    As a result, the prevalent mindset of designing work for crowd workers
    --- one which treats micro task workers as
    ``modular, protocol--defined computational services'' ---
    has inexorably alienated workers from the greater context of their work
    \cite{irani2015cultural}.

    \ali{i don't like this section \textit{here}, but i like it in general. what do?}
    \topic{One of the emergent properties of micro--tasks has been the relative cost of
    \textit{finding} worthwhile tasks.}
    The research community has documented and to some extent attempted to intervene in
    the discovery of worthwhile tasks
    \cite{taskSearch}.
    \citeauthor{Cosley:2007:SUI:1216295.1216309}
    attempts to address this by
    directing workers to tasks through
    ``intelligent task routing''
    \cite{Cosley:2007:SUI:1216295.1216309}.
    Much of this work and the work at the periphery of this space, then,
    has focused on
    minimizing the amount of time that people need to spend doing
    anything other than the work for which they are paid.

    What we take away from this and the previous set of work is that
    the value of adopting crowdsourcing for any particular task
    seems to be mediated by two questions:
    \begin{inlinelist}
      \item How long does it take to train workers to do the work in question? and
      \item How long does it take for the worker to do the work?
    \end{inlinelist}
    Minimizing these criteria has become
    the overarching motivation of the crowdsourcing work design community
    \cite{cheng2015break,Newell:2016:OMA:2858036.2858490}

  \end{appendices}
}
